On Secure Delegation of SampBQP with a Classical Client

### 2020-02-06 bqp.tex
Work some more on Skype meeting results

Let $L\in\BQP$, and $x\in\set{0,1}^n$.
We start with an overview of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.
We'll summarize some more relevant details of this construction in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.

\begin{protocol}{Verifying yes-instances for $\BQP$}
	\label{proto:BQP}
	\begin{enumerate}
		\item The verifier chooses some tensor product of $X$ and $Z$ measurements $\Lambda$
		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit.
		\item The verifier measures $\rho$ according to $S$
		\item The verifier decides whether to accept based on the measurement results.
	\end{enumerate}
\end{protocol}

@@

Mahadev's protocol compiles QPIP1 to QPIP0 but deteriorates soundness, and \cite{parallelrep} says parallel repetition works to recover good soundness guarantees.
\Ethan{TODO elaborate}

>>>>

Let $L\in\BQP$, and $x\in\set{0,1}^n$.
We start with an overview of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.

\begin{protocol}{Verifying yes-instances for $\BQP$}
	\label{proto:BQP}
	We give only a high-level description here.
	\begin{enumerate}
		\item The verifier chooses some tensor product of $X$ and $Z$ measurements $\Lambda$
		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit.
		\item The verifier measures $\rho$ according to $S$
		\item The verifier decides whether to accept based on the measurement results.
	\end{enumerate}
	More details are given later in \cref{AlgGroundStateCheck} where we generalize this protocol for $\SampBQP$.
	\Ethan{TODO clear up details regarding amplification}
\end{protocol}

@@

Mahadev's protocol compiles $\QPIP_1$ protocols of the form in \cref{proto:BQP} to $\QPIP_0$ but deteriorates soundness.
Note that \cref{proto:BlindBQP} can also be written in the four-step form, so the compiler can also be applied to it.
\cite{parallelrep} says parallel repetition works to recover the soundness guarantees.

So we get...
